---
title: "Tarea 1"
author: "Thorvaldur"
date: "9/16/2021"
output: html_document
---
## 1)
#### Making a vector called dado_honesto
```{r}
library(tidyverse)

```
```{r}
dado_honesto=sample(1:6, size=100, replace=TRUE)
show(dado_honesto)

```
#### Calculating the abs and rel frequencies
```{r}
absfr =table(dado_honesto )
show(absfr)

relfr= table(dado_honesto)/length(dado_honesto)
show(relfr)
```



#### Combining both the frequencies into one table
```{r}
total <- rbind(absfr, relfr)
rownames(total) = c("Absolute frequency", "Relative Frequency")

show(total)

```
#### Making a new vector where the number 6 is twice as likely to be chosen than 1-5

```{r}
dado_cargado = sample(1:6, size = 100, replace = TRUE, prob = c(1, 1, 1, 1, 1, 2))
show(dado_cargado)

```
```{r}
absfr1=table(dado_cargado)
show(absfr1)

relfr1= table(dado_cargado)/length(dado_cargado)
show(relfr1)
```

#### Table with the frequencies
```{r}
total1 <- rbind(absfr1, relfr1)
rownames(total1) = c("Absolute frequency", "Relative Frequency")

show(total1)
```


#### Using the seq and rep functions to make vectors
```{r}
vector=rep(1:5,1:5)
show(vector)
vector1=rep(1:4,4)
show(vector1)
```



## 2)

```{r}
ft <- read_csv("Diabetes.csv")
x <- spec(ft)



```

#### Arrange both genders in 3 different age groups and then making a table with abs- and rel frequencies
```{r}
ft$ageGroup <-
  ifelse(ft$age<=40, "1",
         ifelse(ft$age>40 & ft$age<=70, "2",
                ifelse(ft$age>70 & ft$age<=100, "3","NA")))








absf =table(ft$ageGroup)


relf= table(ft$ageGroup)/length(ft$ageGroup)


ageGroup_table <- rbind(absf, relf)
rownames(ageGroup_table ) = c("Absolute frequency", "Relative frequency")

show(ageGroup_table)
```


#### Changing units and calculating BMI
```{r}
ft$weight<- ft$weight*0.454
ft$height <- ft$height*0.0254

ft$BMI <- (ft$weight/(ft$height)^2)
```
#### Ranking people in weight group according to the BMI scale
```{r}
ft$ BMIcat <-
  ifelse(ft$BMI<18.5, "Underweight",
         ifelse(ft$BMI>=18.5 & ft$BMI<25, "Normal Weight",
                ifelse(ft$BMI>=25 & ft$BMI<30, "Overweight",
                       ifelse(ft$BMI>=30, "Obesity","NA"))))
```
#### Making a bar chart that shows how many people are in each BMI group
```{r}
BMIgroup= table(ft$BMIcat)
BMIgroup

barplot(BMIgroup, main="BMI Group Distribution",
   xlab="BMI Group",col=c("darkblue","red"))

```

#### Finding the mean value of BMI and cholesterol of women in every age group
```{r}
bmi1=mean(ft$BMI [ft$gender=="female" & ft$ageGroup=="1"] , na.rm = TRUE)
chol1=mean(ft$chol [ft$gender=="female" & ft$ageGroup=="1"] , na.rm = TRUE)
show(bmi1)
bmi2=mean(ft$BMI [ft$gender=="female" & ft$ageGroup=="2"] , na.rm = TRUE)
chol2=mean(ft$chol [ft$gender=="female" & ft$ageGroup=="2"] , na.rm = TRUE)

bmi3=mean(ft$BMI [ft$gender=="female" & ft$ageGroup=="3"] , na.rm = TRUE)
chol3=mean(ft$chol [ft$gender=="female" & ft$ageGroup=="3"] , na.rm = TRUE)

WomenBmi <- rbind(bmi1,bmi2,bmi3) 

colnames(WomenBmi ) = c("Mean BMI")
rownames(WomenBmi)=c("Group1", "Group2", "Group3")

WomenBmi

WomenChol <- rbind(chol1,chol2, chol3) 

colnames(WomenChol ) = c("Mean Chol")
rownames(WomenChol)=c("Group1", "Group2", "Group3")

WomenChol


















```


#### Here we can see the distribution of BMI by gender in every age group
```{r}
ggplot(ft, aes(x=gender, y=BMI, color=ageGroup))+geom_point() +facet_wrap(~ft$ageGroup)+ labs(x="Gender", y="BMI")
```

#### Distribution of cholesterol
```{r}
ggplot(ft, aes(x=gender, y=chol, color=ageGroup))+geom_point() +facet_wrap(~ft$ageGroup)+ labs(x="Gender", y="Cholesterol")
```



## 3)

#### I did not manage to make an integral & non-zero vector nor get the function to work

```{r}
cambiosSigno=sample(-15:15, size=20, replace=TRUE)
show(cambiosSigno)

signchange <- function(x) {
    index = 0
   
    boolean
     for(i in 1:length(x))
    {
        if(x[i] < 0)
        {
            return (index)
        }
        else
        {
            index = index +1
        }
    }
    
}

signchange(cambiosSigno)

```

